Normalization

### 2023-03-08 reports/03_normalize_data.Rmd
change GEO url

#################
# DOWNLOAD DATA #
#################
## TRX DATA:
GEO_url <- "https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE194276&format=file&file=GSE194276%5FRaw%5Fgene%5Fcounts%5Fmatrix%2Ecsv%2Egz"
# download.file(GEO_url, paste0("../data/"," Raw_gene_counts_matrix.csv.gz"), method="auto")
# system("gunzip ../data/*.gz")

>>>>

#################
# DOWNLOAD DATA #
#################
## TRX DATA:
GEO_url <- "https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE217237"
# download.file(GEO_url, paste0("../data/"," Raw_gene_counts_matrix.csv.gz"), method="auto")
# system("gunzip ../data/*.gz")
